\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
%\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[2]{
  %\item\small{
  \small{
    \textbf{#1}{: #2 \vspace{3pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

%%%%%%%DIY-START
\newcommand{\resumeItemChg}[2]{
	\item\small{
		\textbf{#1}{#2 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubheadingSimple}[2]{
  \vspace{-2pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 
    \end{tabular*}\vspace{-9pt}
}

\newcommand{\resumeItemChgAwa}[2]{
	\item[]\small{
		\textbf{#1}{#2 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubItemChg}[2]{\resumeItemChg{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubItemChgAwa}[2]{\resumeItemChgAwa{#1}{#2}\vspace{-4pt}}
%%%%%%%DIY-END

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}
\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1em]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=1em]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-8pt}}

\newcommand{\skillSectionStart}{\begin{itemize}[leftmargin=0pt]\vspace{-5pt}}
\newcommand{\skillSectionEnd}{\end{itemize}\vspace{-14pt}}


%-------------------------------------------
\begin{document}
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


%----------HEADING-----------------
\centering{\textbf{\LARGE Zehao (Zach) Guan}} \\
\vspace{3.5pt}
\centering{\href{mailto:zehaog@cs.cmu.edu}{zehaog@cs.cmu.edu} $|$ (412) 641-0276}
\\
\centering{\href{https://www.linkedin.com/in/zach-guan/}{linkedin.com/in/zach-guan} $|$ \href{https://www.github.com/zach96guan/}{github.com/zach96guan}}


%-----------EDUCATION-----------------
\vspace{-10pt}
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Carnegie Mellon University}{Pittsburgh, PA}
      {M.S. in Artificial Intelligence and Innovation, School of Computer Science, GPA: 3.83/4.0}{May 2020}
    \vspace{0.5pt}
    \resumeSubheading
      {Zhejiang University}{Hangzhou, China}
      {B.E. in Information Engineering, School of Information and Electronic Engineering, GPA: 3.76/4.0}{Jun. 2018}
  \resumeSubHeadingListEnd
  

%--------PROGRAMMING SKILLS------------
\section{Skills}
\skillSectionStart
        \resumeSubItem{Coursework}
        {Distributed Systems, Practical Data Science, Scalable Machine Learning, Natural Language Processing(TA), Deep Learning, Machine Learning, Text Mining, AI Engineering, Intro to Computer Systems, Database Systems.}
        \newline
		\resumeSubItem{Languages}
		{Python(various data science libraries), Java, C/C\texttt{++}, JavaScript, SQL, Scala, Assembly.}
		\newline
		\resumeSubItem{Tools}
		{Linux, Git, AWS, K8s, MySQL, MongoDB, Hive, MapReduce, HDFS, Spark, TensorFlow, PyTorch, MATLAB.}
\skillSectionEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Walmart Labs}{Sunnyvale, CA}
      {Machine Learning Engineer Intern, Personalization Team}{May 2019 -- Aug. 2019}
      \resumeItemListStart
        \vspace{1.5pt}
        \resumeItemChg{}
        {Designed a personalized recommender for implicit data, and developed latent factor model based collaborative filtering, including pointwise/pairwise non-negative matrix factorization and factorization machine methods.}
        \resumeItemChg{}
        {Aggregated million-scale Walmart.com transaction data by Hive, extracted and preprocessed raw data with PySpark.}
        \resumeItemChg{}
        {Visualized insights from sampled data by Tableau and utilized t-SNE and K-means to analyze latent representations.}
        \resumeItemChg{}
        {Applied ranking information retrieval metrics such as Hit Ratio, Mean Average Precision and Normalized Discounted Cumulative Gain in Python for graded relevance evaluation based on the customers preference.}
      \resumeItemListEnd
    \vspace{3pt}
    
    \resumeSubheading
      {University of Michigan}{Ann Arbor, MI}
      {Research Assistant, Electronic Engineering and Computer Science Dept.}{Jul. 2017 -- Oct. 2017}
      \resumeItemListStart
        \vspace{1.5pt}
        \resumeItemChg{}
        {Developed a prototype system integrated with wearable sensors and remote monitor display for U-M athletic swimmers.}
        \resumeItemChg{}
        {Assembled varied sensors, Bluetooth module and micro-controller on Arduino by C\texttt{++} to collect real-time detected biometric data, and utilized Eagle to redesign schematics and circuit layouts to improve communication efficiency.}
        \resumeItemChg{}
        {Designed Android App to receive transmitted data and multi-thread programs to establish synchronous connections.}
      \resumeItemListEnd
    \vspace{3pt}
      
    \resumeSubheading
      {Nokia Siemens Networks Co., Ltd.}{Hangzhou, China}
      {Software Engineer Intern}{Aug. 2016 -- Nov. 2016}
      \resumeItemListStart
        \vspace{1.5pt}
        \resumeItemChg{}
        {Implemented image processing, segmentation and feature extraction by OpenCV in Python, and applied CNNs based model to build a human face recognition system in TensorFlow.}
        \resumeItemChg{}
        {Embedded the framework in Raspberry Pi with JSON-based front-end display interface to complete a human-machine interactive demo, which is capable of pushing customized information of recognized targets.}
        \resumeItemChg{}
        {Created an open source platform for mobile development on IoT and succeeded in application for Utility Model Patent.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
  

%-----------PROJECTS-----------------
\section{Selected Projects}
  \resumeSubHeadingListStart
      \resumeSubheadingSimple
      {Speech-to-Text Transcription System}{\textit{\small{Feb. 2019 -- Apr. 2019}}}
      \resumeItemListStart
        \vspace{3pt}
        \resumeItemChg{}
        {Developed Attention-based deep neural networks in PyTorch, with a combination of RNNs, CNNs and Dense Nets to design an End-to-End system for speech utterance to corresponding text transcription.}
        \resumeItemChg{}
	    {Evaluated on WSJ dataset with the Levenshtein distance and perplexity, and ranked top 5\% on Kaggle leaderboard.}
      \resumeItemListEnd
      \vspace{3pt}
  
      \resumeSubheadingSimple
      {Question Generation \& Answering System}{\textit{\small{Sept. 2018 -- Nov. 2018}}}
      \resumeItemListStart
        \vspace{3pt}
        \resumeItemChg{}
        {Designed a Q&A system to generate/answer questions from the source of Wikipedia articles based on linguistic features.}
        \resumeItemChg{}
	    {Applied sentence segmentation, Porter stemming and tokenization by spaCy, parsed POS taggers and NER recognition by dependency tree, transformed declarative sentences to ranked binary/WH questions.}
	    \resumeItemChg{}
	    {Utilized scikit-learn to preprocess and vectorize input sentences, identified question types and coreference resolution, calculated Jaccard similarity and TF-IDF relevance to select top candidates for answering.}
      \resumeItemListEnd
      \vspace{3pt}
      
      \resumeSubheadingSimple
      {Intro to Computer Systems Labs}{\textit{\small{May 2018 -- Aug. 2018}}}
      \resumeItemListStart
        \vspace{3pt}
        \resumeItemChg{}
        {Wrote a general-purpose cache simulator, and optimized a small matrix transpose kernel to minimize number of misses.}
        \resumeItemChg{}
	    {Realized a simple Unix shell that supports basic commands of job control and implemented I/O redirection.}
	    \resumeItemChg{}
	    {Implemented a dynamic memory allocator by designing segregated free list and manipulating bits in header/footer with LIFO and best-fit policy, to improve both space utilization and throughput.}
	    \resumeItemChg{}
	    {Built a concurrent HTTP proxy that caches recently accessed web objects to handle multiple client requests in parallel.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
 	
%%%%%%  CV ENDS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
